### 2025-05-08 futureWork/rlHedging.tex
new

In the context of hedging \gls{va} contracts, the state space is partially observed.
The agent does not have access to the contract specifications and the underlying risk factors.
Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
To address the non-Markovian dynamics, an \gls{lstm} component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
This approach is known as recurrent \gls{ppo}~\citep{ni2021recurrent}.
Let $h_t$ be the hidden state of the \gls{lstm} at time $t$.
The state representation $\mathbf{s}_t$ is fed into the \gls{lstm} at each time step to update the hidden state $h_t$.
\begin{equation} \label{eq3:stateRNN}
    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1}),
\end{equation}
where 
\begin{align} 
    h_t &= o_t \odot \tanh(c_t), \nonumber \\
    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \nonumber \\
    i_t &= a(W_i \mathbf{s}_t + U_i h_{t-1} + b_i), \nonumber \\
    f_t &= a(W_f \mathbf{s}_t + U_f h_{t-1} + b_f), \nonumber \\
    o_t &= a(W_o \mathbf{s}_t + U_o h_{t-1} + b_o), \nonumber \\
    g_t &= a(W_g \mathbf{s}_t + U_g h_{t-1} + b_g), 
\end{align}
In a \gls{lstm}, the cell state $c_t$ stores a representation of historical information up to time $t$.
It is updated at each time step by a forget gate $f_t$, an input gate $i_t$, and an output gate $o_t$.
Equation~\ref{eq:lstm} provides a general intoduction to \gls{lstm} for a generic time series input $x_t$.

>>>>

In the context of hedging \gls{va} contracts, the state space is partially observed.
The agent does not have access to the contract specifications and the underlying risk factors.
Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
To address the non-Markovian dynamics, an \gls{lstm} component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
This approach is known as recurrent \gls{ppo}~\citep{ni2021recurrent}.
Let $h_t$ be the hidden state of the \gls{lstm} at time $t$.
The state representation $\mathbf{s}_t$ is fed into the \gls{lstm} at each time step to update the hidden state $h_t$.
\begin{equation} \label{eq3:stateRNN}
    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}), \quad h_t = \text{LSTM}(\mathbf{s}_t, h_{t-1}),
\end{equation}
where 
\begin{align} 
    h_t &= o_t \odot \tanh(c_t), \nonumber \\
    c_t &= f_t \odot c_{t-1} + i_t \odot g_t, \nonumber \\
    i_t &= a(W_i \mathbf{s}_t + U_i h_{t-1} + b_i), \nonumber \\
    f_t &= a(W_f \mathbf{s}_t + U_f h_{t-1} + b_f), \nonumber \\
    o_t &= a(W_o \mathbf{s}_t + U_o h_{t-1} + b_o), \nonumber \\
    g_t &= a(W_g \mathbf{s}_t + U_g h_{t-1} + b_g), 
\end{align}
In a \gls{lstm}, the cell state $c_t$ stores a representation of historical information up to time $t$.
The variables $i_t, f_t, o_t, g_t, c_t, h_t$ are an input gate, a forget gate, an output gate, a cell input, a cell state, and a hidden state at time $t$, respectively.
$W_i$, $W_f$, $W_o$, $W_g$, $U_i$, $U_f$, $U_o$, $U_g$ are weight matrices, and $b_i$, $b_f$, $b_o$, $b_g$ are bias vectors.
$a$ is the activation function, typically a sigmoid function 
\begin{equation} \label{eq3:sigmoid}
    a(x) = \frac{1}{1 + e^{-x}}.
\end{equation}
$\odot$ denotes an element-wise multiplication.
Section~\ref{subsec:LSTM} provides a general intoduction to \gls{lstm} for a generic time series input $x_t$.
